### 2014-10-20 paper/relatedwork.tex
adding some changes

Spark Streaming \cite{boyd2011distributed} introduces a concept of discretized streams to imporve the throughput. Spark streaming processes data as batches while storing them as RDDs \cite{agarwal2011reliable}. Through the usage of RDDs\cite{agarwal2011reliable} it provides fault tolerance without explicitly replicating events in upstream nodes or other nodes. Compared to event based processing systems discretized streams introduces higher latances which may not acceptable for some applications. MillWheel\cite{zaharia2013discretized} is the stream processing system used at Google to process web queries. MillWheel provides relaiable message processing as well as state persistance for its graph based computations. MillWheel treat messages as binary messages leaving message parsing and serialization to application layer.

>>>>

Spark\cite{boyd2011distributed} introduces its RRDs\cite{zaharia2012resilient} to achive better fault tolarance by storing the operations and replaying them instead of replicating data itself or use checkpointing to store data periodically. Spark Streaming\cite{murray2013naiad} extends this concept to distributed stream processing with the concept of discretized events. Spark streaming\cite{murray2013naiad} processes data as batches while storing them as RDDs \cite{agarwal2011reliable} to achive higher throughput. This batch processing may introduce latances which are not acceptable for some applications. Further it is not clear how to implement complex event processing algorithumns such as we use our bench marks with Spark Streaming. MillWheel\cite{zaharia2013discretized} is the stream processing system used at Google to process web queries. MillWheel provides relaiable message processing as well as state persistance for its graph based computations. Unlike in our system MillWheel treat messages as binary messages leaving message parsing and serialization to application layer.

### 2014-10-20 paper/system_architecture.tex
adding the paper in correct format
adding some changes

\section{System Design}
In this section we elaborate the underling system design which is capable of processing 2.4 million messages per second. We emphazise three features of this design. Firstly between any two nodes there is a set of tcp connections (typically 20 connections)  to send messages. All processes share the same set of connections which we called as the bridge. The advantage of this approach compared to having tcp connections per process is that it utilizes all available bandwidth even there is only one process per node. However since this is a common bridge now we need to send receiving process id to dispatch the message, sending  process id to parse the message and sequence number to order messages. As we show latter our experiments shows this approach perform several times better than the other systems dispite above overhead. Secondly we have implemented java.io.OutputStream and java.io.InputStream interfaces on top of java.nio API. Using these input and output streams we provide java.io.DataOutput and java.io.
DataInput 
objects to directly serialize message data to binary format to without sending any metadata along the message. As we explained in earlier section our Event interface provides these methods. Finally except messages itself all the other objects used to send the messages and parse the messages are not created at message processing time. When a process sends the first message all these objects are created and it is a one time cost. Rest of this section further explain how we have implemented above techniques.
\subsection{Inter Process Communication}
Figure \ref{interprocess} shows the design involves in sending a message from one process to another. Lets assume there is a message object at a client side process and that process wants to send this message to another process. First client process sends this message to its ElementContainer. ElementContainer holds all the streams (this is an abstraction of a link in the process graph) to which this message needs to send and it push the message to all streams. Stream object decides which node to send this message and pass the message along the taget node details to ConnectionManager which holds ClientConnection object for each node. ConnectionManager picks the correct ClientConnection for target node and sends the message to ClientConnection. ClientConnection picks an available DataOutput object and invokes the serialize method of the message to send that to server side.

At the server side there are a set of ServerTasks which read receiving messages at DataInput streams available in the ServerConnection (we register these connections at the connections creating time). Once a server task receives a binary message, it creates the event object using the sending process id to identify the event type. Then it pass this message to the WorkerContainer which holds all processes. Finally WorkerContainer dispatch this message to correct process uisng receiving process id. Message ordering happens at the process level if required. This elastrates how we have shared a pool of tcp connections among process and next we show how we have implemented java.io.OutputStream and java.io.InputStream without creating objects dynamically. 
\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{interprocess.png}
        \caption{Communication between two Process}
        \label{interprocess}
\end{figure}
\subsection{Client Side}
Figure \ref{client} shows how we have implemented java.io.OutputStream interface using our DataWriter class. DataWriter contains a java.nio.ByteBuffer object. When a higher layer method writes data to DataOuput object, DataWriter put those bytes to its byte buffer. When a selection event occurs, Datawriter writes its byte buffer to under line SocketChannel. This way we use one byte buffer as a intermediatory create an output stream with java.nio API.
\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{client.png}
        \caption{OutputStream Implementation}
        \label{client}
\end{figure}
\subsection{Server Side}
Figure \ref{server} shows how we have implemented java.io.InputStream interface using our DataReader class. Similar to clinet side, DataReader object has a java.nio.ByteBuffer object. When a selection event occurs DataReader input bytes from the SocketChannel to its byte buffer. When a ServerTask reads data through DataInput, it reads data from the byte buffer and passes to higher layer. In this way we have implemented an input stream with java.nio API.
\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{server.png}
        \caption{InputStream Implementation}
        \label{server}
\end{figure}

>>>>

\section{System Design}
In this section we elaborate the underling system design which is capable of processing 2.4 million messages per second. We emphazise three features of this design. Firstly between any two nodes there is a set of tcp connections (typically 20 connections)  to send messages. All processes share the same set of connections which we called as the bridge. The advantage of this approach compared to having tcp connections per process is that it utilizes all available bandwidth even there is only one process per node. However since this is a common bridge now we need to send the receiving process id to dispatch the message, sending  process id to parse the message and sequence number to order messages. As we show latter our experiments shows this approach perform several times better than the other systems dispite above overhead. Secondly we have implemented java.io.OutputStream and java.io.InputStream interfaces on top of java.nio API. Using these input and output streams we provide java.io.DataOutput and java.io.DataInput 
objects to directly serialize message data to binary format to without sending any metadata along the message. As we explained in earlier section our Event interface provides these methods. Finally except messages itself all the other objects used to send the messages and parse the messages are not created at message processing time. When a process sends the first message all these objects are created and it is a one time cost. Rest of this section further explain how we have implemented above techniques.
\subsection{Inter Process Communication}
Figure \ref{interprocess} shows the design involves in sending a message from one process to another. Lets assume there is a message object at a client side process and that process wants to send this message to another process. First client process sends this message to its ElementContainer. ElementContainer holds all the streams (this is an abstraction of a link in the process graph) to which this message needs to send and it push the message to all streams. Stream object decides which node to send this message and pass the message along the taget node details to ConnectionManager which holds ClientConnection object for each node. ConnectionManager picks the correct ClientConnection for target node and sends the message to ClientConnection. ClientConnection picks an available DataOutput object and invokes the serialize method of the message to send that to server side.

At the server side there are a set of ServerTasks which read receiving messages at DataInput streams available in the ServerConnection (we register these connections at the connections creating time). Once a server task receives a binary message, it creates the event object using the sending process id to identify the event type. Then it pass this message to the WorkerContainer which holds all processes. Finally WorkerContainer dispatch this message to correct process uisng receiving process id. Message ordering happens at the process level if required. This elastrates how we have shared a pool of tcp connections among process and next we show how we have implemented java.io.OutputStream and java.io.InputStream without creating objects dynamically. 
\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{interprocess.png}
        \caption{Communication between two Process}
        \label{interprocess}
\end{figure}
\subsection{Client Side}
Figure \ref{client} shows how we have implemented java.io.OutputStream interface using our DataWriter class. DataWriter contains a java.nio.ByteBuffer object. When a higher layer method writes data to DataOuput object, DataWriter put those bytes to its byte buffer. When a selection event occurs, Datawriter writes its byte buffer to under line SocketChannel. This way we use one byte buffer as a intermediatory create an output stream with java.nio API.
\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{client.png}
        \caption{OutputStream Implementation}
        \label{client}
\end{figure}
\subsection{Server Side}
Figure \ref{server} shows how we have implemented java.io.InputStream interface using our DataReader class. Similar to clinet side, DataReader object has a java.nio.ByteBuffer object. When a selection event occurs DataReader input bytes from the SocketChannel to its byte buffer. When a ServerTask reads data through DataInput, it reads data from the byte buffer and passes to higher layer. In this way we have implemented an input stream with java.nio API.
\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{server.png}
        \caption{InputStream Implementation}
        \label{server}
\end{figure}

### 2014-10-20 paper/system_overview.tex
adding some changes

\section{System Overview}
Our system mainly consists of a set of processes which receive events, process them and forward to next processes. We use the term adapters for special processes which receive events from out side systems. These processes and adapters forms a graph which represents the way a given event stream being processed within the system. Rest of this section further describes this concept at a user level. In the next section we provide a detail explanation about how we have make this interprocess communication efficient.
\subsection{Process Graph}
A Process graph (Figure \ref{processgraph}) mainly consists of the adapters, processes which does the processing logic and their interaction patterns. Adapters receive events from out side systems and forward them to other processes. Processes process events according to a given logic and emits the generated events either to processes or out side systems.

@@

 The Event interface has a method to get the key for a given event. This key is used in sending messages to next processes as described earlier. Parse and serialize methods of event interface are used to direcly serialize the object state to underline streams. Process interface has a method called onEvent which underline framework invokes when it receives an event to that process. The start method of the adapter interace is invoked by the framework and that can be used to pull events from out side systems onces the system starts. At the initilization time both processes and adapters receive the container object which can be used to send events to other processes. Users can specify the runtime graph to the system using a json file as shown below.

>>>>

\section{System Overview}
Our system mainly consists of a set of processes which receive events, process them and forward to next processes. We use the term adapters for special processes which receive events from out side systems. These processes and adapters forms a graph which represents the way a given event stream being processed within the system. Rest of this section further describes this concept at a user level. Our current implementation does not support fault tolarance and have adapted topoloy concept from twitter storm\cite{twitterStorm} and cluster concept from Yahoo S4\cite{neumeyer2010s4}. In the next section we provide a detail explanation about how we have make this interprocess communication efficient.
\subsection{Process Graph}
A Process graph (Figure \ref{processgraph}) mainly consists of the adapters, processes which does the processing logic and their interaction patterns. Adapters receive events from out side systems and forward them to other processes. Processes process events according to a given logic and emits the generated events either to other processes or out side systems.

@@

 The Event interface has a method to get the key for a given event. This key is used in sending messages to next processes as described earlier. Parse and serialize methods of event interface are used to direcly serialize the object state to underline streams. Process interface has a method called onEvent which underline framework invokes when it receives an event to that process. The start method of the adapter interface is invoked by the framework and that can be used to pull events from out side systems onces the system starts. At the initilization time both processes and adapters receive the container object which can be used to send events to other processes. Users can specify the runtime graph to the system using a json file as shown below.
